Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-08 Article/ici_submm_cloudcorr_simon.tex
Added notes.

\newcommand{\todo}[1]{{\color{red} #1}}
\newcommand{\ynfcs}{y_\text{NFCS}}
\newcommand{\yonfcs}{y^{o}_\text{NFCS}}
\newcommand{\ynfcsi}{y_\text{NFCS, i}}
\newcommand{\yonfcsi}{y^{o}_\text{NFCS, i}}
\newcommand{\y}{\vec{y}}

@@

The approach is demonstrated with use of 89 and 150\,GHz channels (following
\citet{geer2015scatteringindex}), but we mainly explore the cloud correction (of
183\,GHz data) that will be possible when sub-millimetre data will be at hand
in some years. This wavelength region will be introduced by the Ice Cloud
Imager (ICI, \citet{eriksson:towar:20}), but likely also be included in several
smaller missions (such as Artic Weather Satellite (AWS); presented below). The focus on sub-mm channels is motivated by several reasons.  Firstly, the higher frequencies have a higher sensitivity to scattering effects from smaller hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger signal than 183\,Ghz. In some cloudy situations it could be possible that the impact at 183 GHz is of the order of thermal noise and modelling uncertainties, while the impact at 325 GHz is significantly higher. Secondly, the true potential of the QRNN cloud correction approach is likely not revealed if tested on existing data and applying ICI data for cloud filtering has not earlier been discussed. It is also argued that the cloud correction makes it possible to make good use of ICI data already in clear-sky assimilation, a fact that should speed up the use of this novel data source.

A description of data and QRNN is provided in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the applicability of correction scheme to existing sensors, and later its application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions} presents the conclusions from this work and the future outlook.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations. The input data are restricted between $60^{\degree}$S to $60^{\degree}$N, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to $45^\circ$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

As has been shown in \citet{pfreundschuh:aneur:18}, QRNN can be used to solve these type of problems. Instead of a point prediction, as it is typically performed in regression problems, QRNNs learn to
predict a vector of quantiles, which can be used to approximate the distribution
of the predicted quantity conditional on the network inputs. Using QRNNs to
perform probabilistic cloud correction thus not only allows deriving an estimate
for $\ynfcs$ but also for the error of the corrected observations.

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$, the quantiles
approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.

QRNN's are trained to minimize the mean of the quantile loss functions
%
\begin{align}
  \mathcal{L}_\tau(y_\tau, y) &=
  \begin{cases}
    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
    \\
  \end{cases}
\end{align}
%
for all predicted quantile fractions $\tau$, where $\y_\tau$ is the predicted
quantile and $y$ the reference value from the training set. The quantile loss is
used in this study as a performance criterion for the tuning of the hyper
parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In addition to the quantile loss, also the Continuously
Ranked Probability Score (CRPS) is considered. Given a predicted cumulative
distribution function (CDF) $F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a predictions from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution and evaluate the above integral.

The implementation of QRNN is similar to one described in \citet{pfreundschuh:aneur:18}, except that instead of Keras python package, PyTorch, an open source machine learning
library \citep{paszke2017automatic} is used. This version is developed and available as a part of \textit{typhon:tools for atmospheric research} software package [\todo{developer's version??}]. The major challenge for implementing QRNN for the current application was to select high performing neural network architecture. This was obtained through grid search over different hyper-parameter configurations. The details are described in Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The basic construction of both is to individually train for each of the available 183\,GHz channels, using certain input training data. The input data is all-sky brightness temperatures from selected input channels and/or additional data like land/sea mask. The output in both configurations is the posterior distribution of NFCS values for the target 183\,GHz channel. The two configurations differ only by the number of input 183\,GHz channels used in the training process:

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values described over the chosen quantiles. In order to facilitate the interpretation of results, examples of QRNN outputs are shown in Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the predicted quantiles for three different cases. This is in contrast with other conventional correction/filtering methods, which give out only point estimates. However, for most analysis, usually a single point estimate is required. In Bayesian analysis, usually the posterior mean or posterior median are selected as point estimates. In this study, we assume the posterior median to be the best estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN in correctly predicting the point estimate, deviation of the median value from the corresponding true value ($\yonfcs$) is evaluated using common performance indicators like bias, mean absolute error (MAE) and standard deviation (STD). The asymmetry of error distributions around their mean is also calculated through the measure of skewness. For a univariate dataset of length $N$, the Fisher-Pearson coefficient of skewness is defined as: 
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to gauge the complete performance. In a successful QRNN training, QRNN learns to predict not only an accurate point estimate but also the correct underlying uncertainty. An ideal QRNN output should be sharp or in other words, all predicted quantiles should be concentrated in the vicinity of the point estimate. The predicted posterior distribution should also be well calibrated, that is, reflect the a priori probability distribution. A straightforward way to compare the two distributions is to plot the frequency of predictions and frequency of the true value in different prediction intervals. This is also commonly known as calibration plot. In a well-calibrated QRNN model, the calibration plot should follow the straight line y = x. Another way to assess how well the predicted posterior distribution reflects the observed errors is to compare the predicted and observed errors. The predicted error is deviation of a random sample drawn from the posterior distribution to its median. In this study, we analyse both the calibration plot and the predicted errors to assess the correctness of predicted uncertainties.

All evaluation results described in the study have been made on the test dataset.

@@

The posterior distribution of NFCS values obtained from experiment 89+150\,GHz is similar to one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}). The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates from NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are corrected successfully with QRNN, but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative departures due to cloud impact lead to a large negative skewness(-14.34) and high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.09\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training, gives comparable results as 89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter, predictions have the most symmetric error distributions, but the highest spread.

@@

The quantiles given out by QRNN can be used to construct the probability distribution of the predictions in contrast to other correction approaches which give out only point estimates. Examples of the uncertainties given out by QRNN is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error distribution is asymmetric. The predictions over quantiles $-3\sigma$, $-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and $3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently.  
The calibration of the prediction intervals on the testing dataset is displayed in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions follow the y=x line, i.e. they are perfectly calibrated with the a priori distribution. However for the cases with correction greater than 5\,K, the distribution is poorly calibrated for higher quantiles. The curve lies below the y=x line indicating that the prediction intervals are too narrow. This is in agreement with the wide spread of predictions over the  higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such cases are few and filtering them results in well calibrated QRNN predictions.

@@

For other humidity channels, the predicted uncertainties followed similar behaviour and the not shown.

@@

Another advantage of QRNN is estimation of case-specific uncertainties. The predictions over chosen quantiles quantify the underlying uncertainty. The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error. The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution. Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information. Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information. Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases. However the cases with low accuracy are associated with high uncertainty, and can be used with caution.

@@

The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact. This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments. In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data. The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases. Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on. Such cases can be the ones which occur infrequently, or those which lack any orthogonal information. The representation of the former can be improved with larger training datasets. However for the latter, improving their a priori distribution is not trivial. Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance.

>>>>

\newcommand{\todo}[1]{{\color{red} #1}}
\newcommand{\ynfcs}{\vec{y}_\text{NFCS}}
\newcommand{\yonfcs}{\vec{y}^{o}_\text{NFCS}}
\newcommand{\ynfcsi}{\vec{y}_\text{NFCS, i}}
\newcommand{\yonfcsi}{\vec{y}^{o}_\text{NFCS, i}}
\newcommand{\y}{\vec{y}}

@@

The proposed cloud correction scheme makes use of a Quantile Regression Neural
Network (QRNN) to obtain a probabilistic prediction of the NFCS value. Unlike
traditional neural networks techniques, which typically only provide a point
estimate of the target variable, QRNNs are trained to predict an arbitrary set
of quantiles of its Bayesian a posteriori distribution
\citep{pfreundschuh:aneur:18}. The predicted a posteriori distribution 
can then be used to derive an estimate of the NFCS value together with an estimate
of the corresponding uncertainty.

The main focus of this study is the potential of proposed cloud-correction
method using sub-millimetre observations, which will become available
operationally with the launch of the Ice Cloud Imager (ICI,
\citet{eriksson:towar:20}) on board the next generation of polar orbiting
meteorological satellites (MetOP-SG), but will likely also be included in
several smaller missions (such as Artic Weather Satellite (AWS); presented
below). Additionally, we demonstrate the feasibility of the approach based on
observations at 89 and 150\ GHz channels (following
\citet{geer2015scatteringindex}), which are available already today. The focus
on sub-mm channels is motivated by several reasons. Firstly, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors. For high altitude cirrus clouds, these frequencies have a stronger
signal than 183\,Ghz. In some cloudy situations it could be possible that the
impact at 183 GHz is of the order of thermal noise and modelling uncertainties,
while the impact at 325 GHz is significantly higher. Secondly, the proposed
cloud correction methods allows integrating ICI sub-mm observations in
clear-sky data assimilation schemes and thus provides a simple
way to make use this novel data source as soon as it becomes available.

A description of the data used in this study and the QRNN approach is provided
in Sect.\ref{data_methods}. In Sect.~\ref{qrnn_mwhs} we demonstrate the
applicability of correction scheme to existing sensors, and later its
application is extended to include sub-mm channels (Sect.\ref{qrnn_ici}). The
results are discussed in Sect.~\ref{discussions}, and Sect.~\ref{conclusions}
presents the conclusions from this work and the future outlook.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer
Simulator (ARTS, \citet{buehler:artst:18}). CloudSat
\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for
forward simulations. The input data are restricted between $60\unit{^{\degree}}S$ to
$60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky
scenarios are simulated. The complete simulation setup is described in Appendix
\ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are
simulated, respectively. All AWS sensor viewing angles (from $0^\circ$ to
$45^\circ$) are simulated, but the results described in this study are based on
nadir viewing angle. Simulations for all three sensors are noise free, so to
incorporate the measurement uncertainties, whenever needed, gaussian noise is
added to according to the channel NE$\Delta$T (see
Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

@@

As has been shown in \citet{pfreundschuh:aneur:18}, QRNNs can be used to solve
these type of problems. Instead of a point prediction, the QRNN is trained to
predict a vector of quantiles of the distribution of the target variable
conditional on the network input. Using these predicted quantiles, the cumulative
distribution function (CDF) of the target variable can be estimated. QRNNs thus
not only allow to predict a value $\ynfcs$ for the corrected brightness temperatures
but also to estimate the uncertainty of the correction.

For this application, the predicted percentiles are chosen to be
$0.2\%, 3\%, 16\%, 50\%, 85\%, 97\%$ and $99.8\%$. For a Gaussian
distribution with mean $\mu$ and standard deviation $\sigma$, these quantiles
approximately correspond to $\mu -3\sigma, \mu-2\sigma, \mu-\sigma
, \mu, \mu + \sigma, \mu + 2\sigma, \mu + 3\sigma$ and thus allows
estimation of the $\pm 1, \pm 2$ and $\pm 3\sigma$ confidence intervals.

QRNN's are trained to minimize the mean of the sum of the quantile loss functions
%
\begin{align}
  \mathcal{L}_\tau(y_\tau, y) &=
  \begin{cases}
    \tau|y - y_\tau|, & y_\tau < y \\ (1 - \tau)|y_\tau - y|, & \text{otherwise}
    \\
  \end{cases}
\end{align}
%
for all selected quantile fractions $\tau$, where $y_\tau$ is the predicted
quantile and $y$ the reference value from the training or test data . The
quantile loss is used in this study as a performance criterion for the tuning of
the hyper parameters of the QRNN (see Appendix~\ref{appendix:hyperparamter}). In
addition to the quantile loss, also the Continuously Ranked Probability Score
(CRPS) is considered. Given a predicted CDF
$F$ and the reference value $y$, the CRPS is defined as
%
\begin{align}
  \text{CRPS}(F, y) = \int_{-\infty}^{\infty} \left (F(y') - y\right )^2\: dy'.
\end{align}
%
To compute the CRPS for a prediction from a QRNN, the predicted quantiles are
used to derive a piece-wise linear approximation of the CDF of the predicted
distribution.

The implementation of QRNN is similar to the one described in
\citet{pfreundschuh:aneur:18}, except that this version uses PyTorch
\citep{paszke2017automatic} instead of Keras \citep{chollet2015keras} to
implement the underlying neural network. The implementation is available as a
part of version of the Typhon software package \citep{typhonv08}. The major
challenge for implementing QRNN for the current application was to select high
performing neural network architecture. This was obtained through grid search
over different hyper-parameter configurations. The details are described in
Appendix~\ref{appendix:hyperparamter}

\subsubsection{QRNN model configurations}
%
\label{sec:QRNN_configuration}
In the study, two QRNN configurations are formulated for cloud-correction. The
basic construction of both is that a separate network is trained for each
183\,GHz channel to correct. The input data is all-sky brightness temperatures
from selected input channels and/or additional data like land/sea mask. The
output in both configurations is the posterior distribution of NFCS values for
the target 183\,GHz channel. The two configurations differ only by the number of
input 183\,GHz channels used in the training process:

@@

\subsection{Evaluation metrics}
\label{sec:validation}
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/posterior_distribution_I1V.pdf} 
	\caption{Examples showing the predicted quantiles of the conditional distribution of $\ynfcs$ }
	\label{fig:posterior_distribution_I1V}	
\end{figure}
QRNN predictions are posterior probability distribution of the NFCS values
described over the chosen quantiles. In order to facilitate the interpretation
of results, examples of QRNN outputs are shown in
Fig.~\ref{fig:posterior_distribution_I1V}. This example illustrates the
predicted quantiles for three different cases. This is in contrast with other
conventional correction/filtering methods, which give out only point estimates.
However, for most application only a single point estimate is required. In
Bayesian analysis, usually the posterior mean or posterior median are selected
as point estimates. In this study, we chose the posterior median as the point
estimate for the predicted NFCS value ($\ynfcs$). To analyse the ability of QRNN
in correctly predicting the point estimate, deviation of the median value from
the corresponding true value ($\yonfcs$) is evaluated using common performance
indicators like bias, mean absolute error (MAE) and standard deviation (STD).
The asymmetry of error distributions around their mean is also calculated
through the measure of skewness. For a univariate dataset of length $N$, the
Fisher-Pearson coefficient of skewness is defined as:
\begin{equation}
g_1 = 	\frac{\sqrt{N(N-1)}}{N-2} \frac{\sum_{i = 1}^{N}(Y_i - \bar{Y})^3/N}{\sigma^3}
\end{equation}
where $\bar{Y}$ and $\sigma$ are mean and standard deviation of the deviations, respectively.

For probabilistic predictions, accuracy of the point estimate is inadequate to
gauge the complete performance. In a successful QRNN training, QRNN learns to
predict not only an accurate point estimates but also the correct underlying
uncertainty. An ideal QRNN output should be sharp or in other words, all
predicted quantiles should be concentrated in the vicinity of the point
estimate, but at the same time, the predicted posterior distribution should be
well calibrated, that is, the predicted distribution should reflect actually
observed frequencies. A straightforward way to compare the two distributions is
to plot the frequency of predictions and frequency of the true value in
different prediction intervals. This is also commonly known as calibration plot.
In a well-calibrated QRNN model, the calibration plot should follow the straight
line $y = x$. Another way to assess how well the predicted posterior distribution
reflects the observed errors is to compare the predicted and observed errors.
The predicted error is the deviation of a random sample drawn from the posterior
distribution to its median. In this study, we analyse both the calibration plot
and the predicted errors to assess the correctness of predicted uncertainties.

All evaluation results described in the study have been made on the test dataset.
\todo{Is this true for the hyper parameter tuning? Because if this is the
  case, the evaluation should be redone on independent data.}

@@

The posterior distribution of NFCS values obtained from experiment 89+150\,GHz
is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The
median value is chosen as the point estimate (see Sect.~\ref{sec:validation}).
The distribution of point estimates is displayed in
Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to
correct most of the low brightness temperature cases, and overall a good match
with the NFCS simulations is observed. However, QRNN is unable to predict the
lowest clear-sky brightness temperatures, and cases with brightness temperatures
around 260\,K occur frequently. The deviations of point estimates from NFCS
simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large
negative deviations are corrected successfully with QRNN, but residual cloud
impact is evident in the negative tail. Most of these residual cases have
departures less than 10\,K. The corresponding error statistics(see
Sect.~\ref{sec:validation}) are provided in
Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected data, the negative
departures due to cloud impact lead to a large negative skewness(-14.34) and
high bias (-0.84\,K). Training QRNN with 89 and 150\,GHz successfully corrects a
major portion of the cloud affected cases, and the bias is reduced to -0.09\,K.
However, high skewness values indicate a negative tail or uncorrected
departures. Including 118\,GHz in the training, gives comparable results as
89+150\,GHz. With 118\,GHz, the error distributions have lower bias and are more
symmetric, but the MAE and STD remain unaltered. This indicates that the
information from 118\,GHz channels can be beneficial in predicting few cases
correctly, but the overall consequence is not exceptionally different from
89+150\,GHz. Similar is the case with using only 150\,GHz. In the latter,
predictions have the most symmetric error distributions, but the highest spread.

@@

The quantiles given out by QRNN can be used to construct the probability
distribution of the predictions in contrast to other correction approaches which
give out only point estimates. Examples of the uncertainties given out by QRNN
is shown in Fig.~\ref{fig:prediction_uncertainty_mwhs}. The spread of error
distribution is asymmetric. The predictions over quantiles $-3\sigma$,
$-2\sigma$ and $-1\sigma$ are quite sharp and lie close to the median value. In
contrast, the spread of predictions over quantiles $1\sigma$, $2\sigma$ and
$3\sigma$ is wider. Also, cases with very high uncertainty occur infrequently.
The calibration of the prediction intervals on the testing dataset is displayed
in Fig.~\ref{fig:calibration_mwhs}. For the entire dataset, the predictions
follow the y=x line, i.e. the predicted uncertainties are perfectly calibrated
with errors observed on the test data. However for the cases with correction
greater than 5\,K, the distribution is poorly calibrated for higher quantiles.
The curve lies below the y=x line indicating that the prediction intervals are
too narrow. This is in agreement with the wide spread of predictions over the
higher quantiles (Fig.~\ref{fig:prediction_uncertainty_mwhs}). However such
cases are few and filtering them results in well calibrated QRNN predictions.
\todo{This cannot be true. Filtering them, i.e. looking only at values with
  correction < 5k will give predictions with too wide uncertainties, so that the
  calibration will be above the diagonal. I don't think this information is particularly
useful, so I'd suggest removing it.}

@@

For other humidity channels, the predicted uncertainties followed similar
behaviour and are not shown.

@@

Another advantage of QRNN is estimation of case-specific uncertainties. The predictions over chosen quantiles quantify the underlying uncertainty. The analysis of QRNN predicted errors and calibration plots show that QRNN is successful in providing well calibrated probabilistic predictions of the posterior distributions except for few cases associated with high error. The poorly calibrated predictions are a consequence of cases with different underlying a priori distribution. Predictions with high error originate from cases with high cloud impact or cloudy cases with no orthogonal information. Such cases have a significantly distinct a priori distribution as compared to clear cases, which dominate the training dataset and influence the a priori information. Additional information in form of more observational data or additional training inputs is required to improve QRNN prediction accuracy for such cases. However the cases with low accuracy are associated with high uncertainty, and can be used with caution.  
\todo{I could not follow the last sentence.}

@@

The applicability of QRNN based correction to current sensors is demonstrated with MHWS-2 and it is shown that QRNN is partially successful in removing the cloud impact. This is not  an optimal solution, but it is in agreement with what can be achieved with the present instruments. In comparison to existing clear-filtering approaches, QRNN gives comparable or better performance and with minimal rejection of data. The accuracy of QRNN is affected by one single limitation, that is the prediction of ``out of distribution'' cases. Out of distribution cases are those which belong to a different a priori distribution than the one QRNN is trained on. Such cases can be the ones which occur infrequently, or those which lack any orthogonal information. The representation of the former can be improved with larger training datasets. However for the latter, improving their a priori distribution is not trivial. Correcting hydrometeor impact for cases without complete complementary information is a challenge for QRNN and always limit its performance. \todo{Cases without orthogonal information are note what I understand as out-of-distribution samples. Moreover, rare cases are rather a matter of training set size. Nonetheless, it is of course essential that
  the training set distribution reflects reality.}
